### 2025-09-08 spanish/sections/languages.tex
Update languages.tex

\cvskill
{} 
{\textcolor{black}{italiano (habilidades de lectura elementales), francés (habilidades de lectura elementales)}} \\

\cvskill
{Programación \&} 
{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}

\cvskill
{software} 
{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\

>>>>

\cvskill
{} 
{\textcolor{black}{francés e italiano (habilidades de lectura elementales)}} \\

\cvskill
{Programación \&} 
{\textcolor{black}{Python, R, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}

\cvskill
{software} 
{\textcolor{black}{{\scshape HPoP}, Zotero, JabRef, {\LaTeX}, Bib{\TeX}, MS Office, WordPress, Moodle, {\scshape java}, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
